---
title: "The Upcoming Pokemon Crisis Vignette"
author: "Mandy Liesch"
output: github_document
---

# Required Packages

R is a super versatile software, and we are allowed to write many different functions using a suite of packages that make analysis and data science much easier. The required packages are as followed. 

*[`httr` Package](https://cran.r-project.org/web/packages/httr/vignettes/quickstart.html): is a package that provides a wrapper for the curl package, allowing pulling of data from API web pages. 

*[`jsonlinte` Package](https://cran.r-project.org/web/packages/jsonlite/index.html): is a package that interprets and parses the json data output of the APIs.

*[`tidyverse` Package](https://www.tidyverse.org/): is a comprehensive data management package, it includes functions to clean, manipulate, and process data, and is one of the flagships of data science in R.

*[`RCurl` Package](https://cran.r-project.org/web/packages/RCurl/index.html): Like httr, RCurl provides functions to allow one to compose general HTTP requests and work with APIs.

*[`ggplot` Package](https://ggplot2.tidyverse.org/): a comprehensive graphing package from the tidyverse. 

*[`knitr` Package](https://www.r-project.org/nosvn/pandoc/knitr.html): A package that manipulates data to control visual output.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
#load the required packages
require("httr")
require("jsonlite")
require("tidyverse")
require("RCurl")
require("ggplot2")
library(usethis)
library(knitr)
library(rmarkdown)
use_git_config(user.name="Mandy Liesch", user.email="amliesch@ncsu.edu")
```

```{r, eval=FALSE, echo=FALSE}
#code to create the rendering. this chunk is put into the code to knit and
#render the function.
rmarkdown::render("ST558Projecct1.Rmd", 
                  output_format = "github_document", 
                  output_options = list(toc=TRUE, toc_depth = 3, html_preview=FALSE), 
                  output_file = "README.md")
```

# Function Creation
## Type Fuctions

### allPoke(): Returns ALL Pokemon

There are 18 different types of Pokemon. These 18 types apply to both Pokémon and their moves. It is possible for Pokemon to have two different types, but they usually have a primary type. This initial function was created to help the user figure out which type they would like to specify. There are several functions necessary to create the output by type. 

```{r}
#Return all the pokemon names and their informative urls into a dataframe. 
allPoke<-function(){
  ### This function Connects to the Pokemon endpoint, using a limit 
  #to make sure all are returned.
  allPokeURL<-"https://pokeapi.co/api/v2/pokemon?limit=1500"
  #Utilize the RCurl to get all of the json data from the endpoint
  pokeData <- RCurl::getURL(allPokeURL)
  #Parse the JSon data into a list with the content variables
  pokeDataDF<-jsonlite::fromJSON(pokeData)
  #pull all of the important results into the dataframe 
  #(the pokemon name and URL)
  output <- pokeDataDF$results
  #Use the purr package to pull all of the JSON Data for each pokemon
  #URL into a list.
  pokeData1<-purrr::map(output$url, jsonlite::fromJSON)
  #Return this list when the function is called. 
  return(pokeData1)
}

```

### types(): User Defined Type

This function utilizes the Type endpoint to return the information of a type that the user specifies. It has many different layers, and allows the user to input a number from 1-20, that corresponds to a pokemon type, OR a type character string, like 'fire'. If 'all' is specified, a list is returned with all pokemon, from the allPoke() function, listed previously. If an incorrect string or number is put in, a list is returned of appropriate options in Pokemon type.

```{r}
types <- function(type){
  ###
  # This functions returns a data.frame with the numeric key and the name
  # of the types associated with pokemon. It can also return the data for 
  # a single type if a type ID number or name is passed.
  ###
  
  # Get the overall type from the type endpoint, allowing a user specified
  #type.
  baseURL<-"https://pokeapi.co/api/v2/type/"
  # pull the information for all types from the endpoint
  typeData <- RCurl::getURL(baseURL)
  # convert this into a dataframe
  typeDataDF<-jsonlite::fromJSON(typeData)
  # Select and create the type data.frame from the results.
  output <-  typeDataDF$results
  #Create a table to return the type and number in case bad input is
  #specified.
  outputType <- data.frame(type=1:20, output)
  
  #First If Function
  # If type does not equal "all", check if it is a valid pokemon type
  #or numeric value.
  if (type != "all"){
    
    # If type is in the numeric type column, subset output for just that row.
    if (type %in% outputType$type){
      #set the function to query
      pokeType <- type
      #Create the new link to read the user specified API value
      pokeTypeSpec <-GET(paste0(baseURL,pokeType))
      #Run the API through the data, return the JSON
      pokeTypeparsed <- pokeTypeSpec$content %>% rawToChar() %>% fromJSON()
      #Pull the desired data from the pokemon subset of list.
      typeParseRes<-pokeTypeparsed$pokemon
      #Use the purr package to return the json data
      pokePrimary<-purrr::map(typeParseRes$pokemon$url, jsonlite::fromJSON)
      #Return the dataframe.
      return(pokePrimary)
    }
    # If type is in the name column, subset output for just that table, see
    #above for documentation.
    if (type %in% outputType$name){
      pokeType <- type
      pokeTypeSpec <-GET(paste0(baseURL,pokeType))
      pokeTypeparsed <- pokeTypeSpec$content %>% rawToChar() %>% fromJSON()
      typeParseRes<-pokeTypeparsed$pokemon
      pokePrimary<-purrr::map(typeParseRes$pokemon$url, jsonlite::fromJSON)
      return(pokePrimary)
    }
    # Otherwise, if type does not equal all, throw an informative error,
    #return the options table.
    else {
    message <- paste("ERROR: The numeric Index of Pokemon Type, or Pokemon
                     Type is not clear.",
                     "Select from the menu above, or type('all') to find 
                     information of all of the Pokemon Type you're looking
                     for.")
    print(outputType[1:2])
    stop(message)
    }
  }
  #If the user specified the all function, return the output of the allPoke() function.
  else {
  pokePrimary<-allPoke() 
  return(pokePrimary)
  }
}

```


### typeFrame(): Returning Several Columns

The list function dataset is very complex. This nested function turns the user specified type list into the dataframe that we desire. The index value is a numerical input that is used to return the function. Due to speed concerns, I removed this nesting function capability, for processing, requiring data frames to be run with the user specified query. The top lines of code change to: 

```{r, eval=FALSE}
typeFrame<-function(type, index){
  frame<-types(type)  
```

However, for speed reason, this is the function used. The index is a numerical pokemon value. It outputs a single row with 12 columns. 
```{r}
typeFrame<-function(frame, index){
  ###
  # This functions takes the specified type defined by a dataframe in the types function,   # and creates one row of a dataframe by pokemon index number. 
  ###
 
  #for simplification, the indexing process is changed to a shorter command
  agg<-frame[[index]]
  #Pull the data for the pokemon ID. 
  pokeid<-agg$id
  #Pull the data for the pokemon Name.
  pokeName<-agg$name
  #Pull Pokemon Height Data
  pokeHeight<-agg$height
  #Pull Pokemon Weight Data
  pokeWeight<-agg$weight
  #Pull data from Type 1. 
  pokeType1<-agg$types$type$name[1]
  #Pull data from Type 2.
  pokeType2<-agg$types$type$name[2]
  #The stats column for pokemon stats is vertical, and needs to be           #transposed
  #so it fits onto one line. It is the first column of the $stats data.
  stats<-t(agg[["stats"]][1])
  #Create a dataframe
  pokeFinal<-as.data.frame(cbind(pokeid, pokeName, pokeHeight, pokeWeight,
                                 pokeType1, pokeType2, stats))
  #return the dataframe.
  return(pokeFinal)
}

```


### listPrep(): Creating the Complete Dataframe

This function is a wrapper function, that takes the single row output of the typeFrame() function, and repeats it for the entire length of the data frame generated from the type function. 
```{r}
listPrep<-function(typePrep){
  ###
  # This list prep function is a wrapper function that takes in the frame
  #specified by the user specified type functions, and populates the single
  #row from the typeFrame and passes it through the lapply function to get
  #a data frame.
  ###
  
  #To determine the number of repititions, we need to determine the length
  #of the types frame. 
  listLen<-length(typePrep)
  #Create the index to wrap through the lapply function.
  numIndex<-1:listLen
  #Run the typeFrame function on the user specified pokemon type frame the
  #number of times specified in the index.
  finalTypeFrame<-lapply(X = numIndex, FUN = typeFrame, frame=typePrep)
  #Format the lists into a data frame, and return the output.
  finalFrame<-do.call(rbind.data.frame, finalTypeFrame)
  return(finalFrame)
}
```

### cleanFrame(): Processing the Type Data into Columns 

The list prep function creates a data frame, but it is all character data. To utilize this data frame, the column names need to be changed, formatted, and the extras are to be deleted. This function is a wrapper to the listPrep() wrapper function, and generates a fully clean data frame of the user specified type.
```{r}
cleanFrame<-function(typePrep){
  ### The purpose of this function is to take the list run through 
  #lapply,and clean and correct the column formatting so the data can be
  #manipulated with dplyr.
  ###
  lapplyFrame<-listPrep(typePrep)
  #rename the columns to their correct name
  lapplyFrame$hp<-lapplyFrame$`1`
  #change the column type to numeric
  lapplyFrame$hp<-as.numeric(lapplyFrame$hp)
  #remove the old column value.
  lapplyFrame$`1`<-NULL
  #repeat this for all columns that it needs to happen to. 
  lapplyFrame$attack<-lapplyFrame$`2`
  lapplyFrame$attack<-as.numeric(lapplyFrame$attack)
  lapplyFrame$`2`<-NULL
  lapplyFrame$defense<-lapplyFrame$`3`
  lapplyFrame$defense<-as.numeric(lapplyFrame$defense)
  lapplyFrame$`3`<-NULL
  lapplyFrame$specialattack<-lapplyFrame$`4`
  lapplyFrame$specialattack<-as.numeric(lapplyFrame$specialattack)
  lapplyFrame$`4`<-NULL
  lapplyFrame$specialdefense<-lapplyFrame$`5`
  lapplyFrame$specialdefense<-as.numeric(lapplyFrame$specialdefense)
  lapplyFrame$`5`<-NULL
  lapplyFrame$speed<-lapplyFrame$`6`
  lapplyFrame$speed<-as.numeric(lapplyFrame$speed)
  lapplyFrame$`6`<-NULL
  lapplyFrame$pokeHeight<-as.numeric(lapplyFrame$pokeHeight)
  lapplyFrame$pokeWeight<-as.numeric(lapplyFrame$pokeWeight)
  lapplyFrame$pokeid<-as.numeric(lapplyFrame$pokeid)
  return(lapplyFrame)
}  

```

## Generation Functions

### allGen(): Returns All Generations of Pokemon

Like the allPoke() function above, this generation function queries the Pokemon Species Endpoint API to get all of the information available. This is not a function that is user queryable, and is part of the generation function. 

```{r}
allGen<-function(){
  #Connect to the Pokemon Species endpoint, using a limit to make sure all
  #are returned.
  allGenURL<-"https://pokeapi.co/api/v2/pokemon-species?limit=1000/"
  #Utilize the RCurl to get all of the json data from the endpoint
  genData <- RCurl::getURL(allGenURL)
  #Parse the JSon data into a list with the content variables
  genDataDF<-jsonlite::fromJSON(genData)
  #pull all of the important results into the dataframe (the pokemon name
  #and URL)
  output <- genDataDF$results
  #Use the purr package to pull all of the JSON Data for each pokemon URL
  #into a list.
  genData1<-purrr::map(output$url, jsonlite::fromJSON)
  #Return this list when the function is called.
  return(genData1)
}

```

### genOut() Function

This function returns the user specified generational frame, including wrapping in the all functions. It outputs a dataframe of lists that will be run through future functions. Any user specified variables other than the 'all' generations query the Generation endpoint. 
```{r}
genOut <- function(generation){
  ###
  # This functions returns a data.frame with the numeric key and the name
  #of the generations associated with pokemon. It can also return the data
  #for a single generation if a numeric ID of generation is passed.
  ###
  
  # Get the overall generation from the type endpoint, allowing a user
  #specified generation.
  baseURL<-"https://pokeapi.co/api/v2/generation/"
  #pull all of the generation URLs, and put them into a json.
  genData <- RCurl::getURL(baseURL)
  genDataDF<-jsonlite::fromJSON(genData)
  
  # Select and create the generation data.frame from the results.
  output <-  genDataDF$results
  #create the data frame needed for specifying errors.
  outputGen <- data.frame(gen=1:8, output)
  
  # If generation does not equal "all", check if it is a valid pokemon
  #generation or numeric value.
  if (generation != "all"){
    
    # If generation is in the number column, subset output for just that
    #row.
    if (generation %in% outputGen$name){
      #use the user specified value to generate the new API section.
      pokeGen <- generation
      #put the url into the API
      pokeGenSpec <-GET(paste0(baseURL,pokeGen))
      #parse through the data to get the URLs from the API query.
      pokeGenparsed <- pokeGenSpec$content %>% rawToChar() %>% fromJSON()
      #Pull data from the pokemon species subset of the generations.
      genParseRes<-pokeGenparsed$pokemon_species
      #Get the individual pokemon URLs
      genPrimary<-purrr::map(genParseRes$url, jsonlite::fromJSON)
      #Return the list.
      return(genPrimary)
    }
    # If generation is in the generation list column, subset output for
    #just that row.Repeats from above
    if (generation %in% outputGen$gen){
      pokeGen <- generation
      pokeGenSpec <-GET(paste0(baseURL,pokeGen))
      pokeGenparsed <- pokeGenSpec$content %>% rawToChar() %>% fromJSON()
      genParseRes<-pokeGenparsed$pokemon_species
      genPrimary<-purrr::map(genParseRes$url, jsonlite::fromJSON)
      return(genPrimary)
    }
    # Otherwise, throw an informative error to get the appropriate values
    #that occur.
    else {
    message <- paste("ERROR: The number or index of generation chosen is
                     not a valid selection.",
                     "Select from the menu above, of try generation('all')
                     to find the Pokemon and Generation you're looking
                     for.")
    print(outputGen[1:2])
    stop(message)
    }
  }
  #If all is specified, then run the allGen() function that we defined
  #earlier.
  else {
  genPrimary<-allGen() 
  return(genPrimary)
 } 
}

```

### genFrame(): Returning a Single Row of Generations Column

Like the type API, because of the volume of the output potential, the object specified as the genOut() passes through this function as the 'frame' argument, and any number put into the index function returns an individual pokemon's row. This returns a single row

```{r}
genFrame<-function(frame, index){
  ### 
  # This function, like the pokemon type frame, takes the user defined
  # generation data and gets the necessary data from the generation
  # list specified above.
  ###
  
  #This is a function to simplify the process later down the list.
  gen<-frame[[index]]
  #Get the pokemon ID
  pokeid<-gen$id
  #Get the pokemon name.
  pokeName<-gen$name
  #Pull the pokemon generation data
  pokeGen<-gen$generation$name
  #Grab the categorical pokemon growth rate.
  pokeGrowth<-gen$growth_rate$name
  #Pull the pokemon baseline happiness levels. 
  pokeHappy<-gen$base_happiness
  #Get the ease of capture rate
  pokeCapture<-gen$capture_rate
  #Bind everything together into one dataframe.
  pokeGenFinal<-as.data.frame(cbind(pokeid, pokeName, pokeGen, pokeGrowth,
                                    pokeHappy, pokeCapture))
  #return the final row in the data frame.
  return(pokeGenFinal)
}

```

### genListPrep(): Repeat the Generation Function

This function takes the generation function we defined before, and runs it through the lapply function for the entire data frame.

```{r}
genListPrep<-function(genPrep){
  ###
  # This list prep function is a wrapper function that takes in the
  #generation frame specified by the user specified type functions, and
  #populates the single row from the genFrame and passes it through the
  #lapply function to get a data frame.
  ###
  
  #To determine the number of repetitions, we need to determine the length
  #of the generation frame. 
  listLen<-length(genPrep)
  #Create the index to wrap through the lapply function.
  numIndex<-1:listLen
  #Run the genFrame function on the user specified pokemon generation frame
  #the number of times specified in the index.
  finalGenFrame<-lapply(X = numIndex, FUN = genFrame, frame=genPrep)
  #Format the lists into a data frame, and return the output.
  finalGenFrame<-do.call(rbind.data.frame, finalGenFrame)
  return(finalGenFrame)
}

```

### cleanGen(): Cleaning the Generation Dataframe

Like the previous type functions, the generation cleaning frame takes the dataframe that was generated by the user specified generation value, and converts the data into the correct formats. 
```{r}

cleanGen<-function(genPrep){
  ### 
  # The purpose of this function is to take the list run through lapply,
  # and clean and correct the column formatting so the data can be
  # manipulated with dplyr.
  ###
  
  #get the dataframe defined in the genListPrep() function.
  lapplyGen<-genListPrep(genPrep)
  #Convert the character data into numeric data.
  lapplyGen$pokeid<-as.numeric(lapplyGen$pokeid)
  lapplyGen$pokeHappy<-as.numeric(lapplyGen$pokeHappy)
  lapplyGen$pokeCapture<-as.numeric(lapplyGen$pokeCapture)
  #Return the data frame.
  return(lapplyGen)
}

```

## Merging Functions

### mergedFinal(): Merge the type and generation datasets

We have looked at the two main functions that are put together. In order to do final anlysis (in my case), we want to have the generations data set merged together with the pokemon dataset to get our final output creation.

```{r}
mergedFinal<-function(typePrep, genPrep){
  ###
  # This function takes the user defined type output, and generation 
  # output frames and merges them together into one final dataset, that
  # was built from four different APIs.
  ###
  
  #Call the cleaning frame of both the type, and generation.
  typeMerge<-cleanFrame(typePrep)
  genMerge<-cleanGen(genPrep)
  #Merge the files together by both the pokemon ID and pokemon name.
  finalMerge<-merge(typeMerge, genMerge, by=c('pokeid', 'pokeName'),
                    all.y=TRUE)
  return(finalMerge)
}

```


# Data Analysis

## Run the Functions

```{r}
#Running the types function for the user determined function (want 'all'). Specify any of the types that the user wishes is possible (there are 20, for reference).
typeAllFrame<-types('all')
#Run the genOut function to determine the user defined generation data. Specify any geneartion of Pokemon (there are 8, for reference.)
genAllFrame<-genOut('all')
#Run the mergedFinal function to putt together the pokemon id and name, and 14 other desired variables. 
mergedFF<-mergedFinal(typeAllFrame, genAllFrame)
```

## Are Fat Pokemon Happy?
The thousands of different pokemon have an ideal weight and type associated with their species. Poke-scientists have also studied the baseline level of happiness that come when a person first catches a pokemon. Some species are much happier than others. Does this correspond with the pokemons overall weight?

To calculate the pokemon BMI, we need to use the dataframe we returned, and the mutate function to create a new variable called BMI. There is one miserable pokemon (Happiness of 0, with a BMI of nearly 10,000), so we filter out his data, as it is an outlier.
```{r}
mergedFF<- mergedFF %>%
  mutate(BMI = pokeWeight/(pokeHeight*pokeHeight))

plotFF<- mergedFF %>%
  filter(BMI < 50)
```

Then, we can plot the overall happiness of the pokemon, vs their BMI in ggplot2. 

```{r}
plot1 <- ggplot(plotFF, aes(BMI,
                               pokeHappy)) +
  # Add a scatter plot layer and adjust the size and opaqueness of points.
  geom_point(size=3, alpha=0.75) + 
  # Remove the legend.
  theme(legend.position="none") + 
  # Add a black regression line.
  geom_smooth(method=lm, formula=y~x, color="black") + 
  # Add labels to the axes.
  scale_x_continuous("Pokemon BMI") + 
  scale_y_continuous("Pokemon Happiness Level") + 
  # Add a title.
  ggtitle("Baseline Pokemon Happiness and BMI")

plot1

```

It appears that there is a slight negative correlation to baseline happiness to BMI, however, it appears most pokemon are pretty happy, despite their BMI. However, as the following plot shows, even with the super high numbers filtered out, heavier pokemon still have a higher overall sadness level, despite their density. As a super dense, yet heavy human, and not a poke-scientist, I can only speculate that they have bodily wear and tear from using their body, repeatedly in fights, combined with the higher wear and tear of moving and feeding heavy mass. 

```{r}
plot2 <- ggplot(plotFF, aes(pokeWeight,
                               pokeHappy)) +
  # Add a scatter plot layer and adjust the size and opaqueness of points.
  geom_point(size=3, alpha=0.75) + 
  # Remove the legend.
  theme(legend.position="none") + 
  # Add a black regression line.
  geom_smooth(method=lm, formula=y~x, color="black") + 
  # Add labels to the axes.
  scale_x_continuous("Pokemon Weight") + 
  scale_y_continuous("Overall Pokemon Happiness") + 
  # Add a title.
  ggtitle("Fat Pokemon are Less Happy")

plot2

```

##Are Heavy Pokemon Powerful?

Now, we need to look at the overall statistics a pokemon has. This is done by summing all of the attack, defense, speed, and hitpoints

```{r}
#Use dplyr to calculate the total sum of the power statistics
plotFF<- plotFF %>%
  #Add a new column summing six numerical columns together.
  mutate(SUM = rowSums(.[7:12]))

plotFF<- plotFF %>%
  #Calculate the total attack stats in Pokemon.
  mutate(SumAttack = attack + specialattack)

```

Now, in most societies, power tends to be a good thing. And in pokemon, the overall total sum of all of the statistics shows how much power and value a pokemon has. Even though fat pokemon tend to have more power, overall, it appears this level of power really weighs on their mind. The colored circles represent the attack power, and the heavier a pokemon is, the more power it has. 


```{r}
plot3 <- ggplot(plotFF, aes(SUM, pokeWeight, color=SumAttack)) +
  # Add a scatter plot layer and adjust the size and opaqueness of points.
  geom_point(size=3, alpha=0.75) + 
  # Add a color gradient for winPercentage.
  scale_color_gradient(low="blue", high="red") +
  # Remove the legend.
  theme(legend.position="none") + 
  # Add a black regression line.
  geom_smooth(method=lm, formula=y~x^2, color="black") + 
  # Add labels to the axes.
  scale_x_continuous("Sum of All Power Stats") + 
  scale_y_continuous("Pokemon Weight") + 
  # Add a title.
  ggtitle("Heavy Pokemon are More Powerful, Especially in Attack Power (Redder)")

plot3
```

Like in people, big people know they are being used to lift heavy stuff, and pull tall objects off the shelf. These high attack power and higher stat pokemon are likely used in Poke-national defense, and super hard, manual labor jobs, so the fact that heavier pokemon tend to be less happy makes sense. Power is a heavy responsibility and weight these heavy pokemon disproportionately wear.

## Pokemon Weight and Happiness Over Time

So, we have data over multiple generations, showing the avereage weight of pokemon over time. This data can be summerized into categories and shown in a table. 

```{r}
#creating a function to summerize pokemon weight by generation
breakdown <- plotFF %>%
 group_by(pokeGen) %>%
 summarise(Weight = mean(pokeWeight))

#Summerise pokemon Happiness by generations.
breakdown1 <- plotFF %>%
  group_by(pokeGen) %>%
  summarise(Happiness = mean(pokeHappy))

#merge the two data frames together for a numerical table.
fullbreak<-merge(breakdown, breakdown1, by='pokeGen')


```

It appears that, like American Society, pokemon are getting heavier and sadder over time as well, peaking in generation  7, with sadness continuing to decline over time substatially. Generation 4 was both fat, and happy, but the wear of Pokesociety is starting to get to the newer pokemon.  

```{r}
#Create a new table with the pokemon weight and happiness over time.
knitr::kable(
  fullbreak,
  caption=paste("Pokemon Weight and Happiness over Generations"),
  col.names = c("Generation",
                           "Weight",
                           "Happiness"),
  digits=2
)
```

## Does Type Influence Happiness and Weight?

Looking at generational and weight trends, it is possible to look at trends by primary pokemon type.
```{r}

typeWeight<- plotFF %>%
  group_by(pokeType1) %>%
  summarise(Weight = mean(pokeWeight))

typeHappy<- plotFF %>%
  group_by(pokeType1) %>%
  summarise(Happiness = mean(pokeHappy))

typeMerged<-merge(typeWeight, typeHappy, by= 'pokeType1', all=TRUE)


knitr::kable(
  typeMerged,
  caption=paste("Pokemon Weight and Happiness over Different Types"),
  col.names = c("Primary Type",
                           "Weight",
                           "Happiness"),
  digits=2
)
```

The biggest discrepancy between the correlation of weight and type lie with the goth, emo teenagers of the pokemon world: the dark pokemon. They tend to have very low levels of baseline happiness, even though they have an average weight that is around the mean. Dragons and steel type pokemon also tend to be very miserable. Now, if I was a dragon, I would be very happy, what with the massive power, dens, and treasure. However, hoarding generally 

```{r}
#Create a dataframe with generations, types, and weights with the average by type.
typeGenWeight<- plotFF %>%
  group_by(pokeGen, pokeType1) %>%
  summarise(Weight = mean(pokeWeight))

#Summerise pokemon Happiness by generations.
typeGenHap <- plotFF %>%
  group_by(pokeGen, pokeType1) %>%
  summarise(Happiness = mean(pokeHappy))

#
typeBreak<-merge(typeGenWeight, typeGenHap, by=c('pokeGen', 'pokeType1'), all=TRUE)

```

# Conclusions

This Pokemon Vignette uses several built in functions and tidyverse packages to expose the increasing amount of sadness and heavier weights occuring in the Pokemon  Universe over time with visuals, graphs, and tables. This is cutting edge reasearch into newly arising problems in pokemon culture. 
Future research questions include:
* Is this increase in sadness a response to colonial expansion to these new areas in new generations? Or are we just discovering more diverse colony types in harser parts of the world?
* Are these pokemon who are heavy and less happy found in more rural areas?
* Where are the best places to put pokemon intervention centers. 